### 2017-05-13 paper/evaluation.tex
updates

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of individual test cases per project.  We observed
that the average median value of execution cost for a test was
relatively small (dashed horizontal red lines), namely 0.31s for
\medg{} projects and 0.23s for \longg{} projects.  The standard
deviations associated with each distribution were relatively
low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
  specific ranges of $\sigma$ values.}  We noted a small number of
cases of CPU monopolization.  For example, the highest value of
$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
medium group.  This project contains only 65 tests, 62 of which take
less than 0.5s to run, one of which takes nearly 3s to run, and two of
which take $\sim$40m to run.  For this project, 99.2\% of the
execution cost is dominated by only 3\% of the tests; without these
two costly tests this project would have been classified as
short-running.  A closer inspection in the data indicates that the
project \CodeIn{uber\_chaperone} was a corner case; we did not find
other projects with such extreme time monopolization profile.  Project
\CodeIn{facebookarchive\_linkbench} is also classified as long-running
and has the second highest value of $\sigma$.  For this project,
however, cost is distributed more smoothly across \Fix{529} tests, of
which \Fix{119 (23\%)} take more than \Fix{1s} to run with the rest of
the tests running faster.

>>>>

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of individual test cases per project.  We observed
that the average median value of execution cost for a test was
relatively small (dashed horizontal red lines), namely 0.31s for
\medg{} projects and 0.23s for \longg{} projects.  The standard
deviations associated with each distribution were relatively
low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
  specific ranges of $\sigma$ values.}  We noted a small number of
cases of CPU monopolization.  For example, the highest value of
$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
medium group.  This project contains only 65 tests, 62 of which take
less than 0.5s to run, one of which takes nearly 3s to run, and two of
which take $\sim$40m to run.  For this project, 99.2\% of the
execution cost is dominated by only 3\% of the tests; without these
two costly tests this project would have been classified as
short-running.  A closer inspection in the data indicates that the
project \CodeIn{uber\_chaperone} was a corner case; we did not find
other projects with such extreme time monopolization profile.  Project
\CodeIn{facebookarchive\_linkbench} is also classified as long-running
and has the second highest value of $\sigma$.  For this project,
however, cost is distributed more smoothly across \Fix{98} tests, of
which \Fix{8 (8.1\%)} take more than \Fix{1s} to run with the rest of
the tests running faster.
